A tool set for random number generation on GPUs in R

### 2021-12-22 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
paper1
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3058 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{A summary of the results}
We summarized the comparison results in the table \ref{tab:summary} and plot the test statistics in Figure %\ref{fig4}.
<<summarycompare, echo=FALSE, eval=TRUE, cache=TRUE, fig.pos='h'>>=
library(kableExtra)
dt <- data.frame(
  var1 = c("B", "1M", "10M", "1M", "10M"),
  var2 = c('Intel 2.5ghz', 0.403804, 0.0001251, 10.74,  63.24),
  var3 = c('AMD Radeon', 0.403507, 0.0001274,   2.28,    10.82),
  var4 = c('Intel 3.7ghz', 0.4035606,0.0001202, 14.48,  91.00),
  var5 = c('NVIDIA V100', 0.403507,0.0001274,   0.32,   1.95),
  var6 = c('Data','month','week','month','week')
)

>>>>

\subsection{A summary of the results}
We summarized the comparison results in the table \ref{tab:summary} and plot the test statistics in Figure %\ref{fig4}.
<<summarycompare, echo=FALSE, eval=TRUE, cache=TRUE, fig.pos='h'>>=
library(kableExtra)
dt <- data.frame(
  var1 = c("B", "1M", "10M", "1M", "10M"),
  var2 = c('Intel 2.5ghz', 0.403804, 0.0001251, 10.74,  63.24),
  var3 = c('AMD Radeon', 0.403507, 0.0001274,   2.28,    10.82),
  var4 = c('Intel 3.7ghz', 0.4035606,0.0001202, 14.80,  92.00),
  var5 = c('NVIDIA V100', 0.403507,0.0001274,   0.32,   1.95),
  var6 = c('Data','month','week','month','week')
)
